Adolescent well-being in the digital age

### 2022-04-08 00-describe.Rmd

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  group_by(Dataset, region, outcome, country) %>% 
  summarise(
    n_n = sum(n),
    n_year = length(unique(year))
  ) %>% 
  summarise(
    N = sum(n_n), 
    Years = mean(n_year)
  ) %>%
  summarise(
    N_sum = round(mean(N)), 
    Years_mean = round(mean(Years))
  ) %>%
  kbl(caption = "Dataset summary") %>% 
  kable_custom()
gwp %>% 
  group_by(outcome) %>% 
  summarise(n=sum(n)) %>% 
  summarise(N=comma(median(n)))
```

@@

```{r}
unique(gwp$age)
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome)
itu %>% 
  drop_na(internet)

@@

>>>>

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  group_by(Dataset, region, outcome, country) %>% 
  summarise(
    n_n = sum(n),
    n_year = length(unique(year))
  ) %>% 
  summarise(
    N = sum(n_n), 
    Years = mean(n_year)
  ) %>%
  summarise(
    N_sum = round(mean(N)), 
    Years_mean = round(mean(Years))
  ) %>%
  kbl(caption = "Dataset summary") %>% 
  kable_custom()
tmp <- gwp %>% 
  group_by(outcome) %>% 
  summarise(n=sum(n)) %>% 
  summarise(N=comma(median(n))) %>% 
  pull(N)
```

The median number of respondents per (well-being) outcome was `r tmp`, and the unique age bins in the GWP data were `r unique(gwp$age)`.

@@

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome) %>% 
  kbl(caption = "Observations per outcome") %>% 
  kable_custom()

@@

Number of ITU observations

```{r}
tmp <- itu %>% 
  select(region, country, year, internet, mobile)
tmp %>% 
  drop_na(mobile)
```
